The \kplr\ Catalog: Systematic probabilistic parameter estimation for every \kepler\ planet candidate

### 2013-11-27 document/ms.tex
duration tweaks

@@

>>>>

\section{Parameters}

We choose to sample in parameters that are directly informed by the light
curve instead of the full set of physical parameters in the generative model.
The motivation for this choice is to attempt to find parameters that are close
to sufficient statistics for the light curves while being independent of the
stellar parameters.
To this end, we chose to parameterize each planet candidate with period
\period, epoch \epoch, radius \ror\ (measured in stellar radii), impact
parameter \impact, and transit duration \duration.
Our specific definition of transit duration deserves some discussion.
We define the transit duration as the time that it would take for the
center of the exoplanet to transit the center of the star (at $b=0$) instead
of choosing one of the standard definitions---for example $T_\mathrm{tot}$
from \citet{winn}.
We make the further simplifying assumption that the planet transits in a
straight line across the face of the star (WORDING).
In this limit, the conversion between \duration\ and the standard
$T_\mathrm{tot}$ used in the KOI catalog is
\begin{eqnarray}
T_\mathrm{tot} \approx \duration \, \sqrt{(1+\ror)^2 - \impact^2}
\end{eqnarray}

\section{Comments}

\begin{itemize}
\item{Limb darkening}
\item{Integration over exposure time}
\end{itemize}

@@

\bibitem[Winn(2010)]{winn}
Winn, J.~N.\ 2010, \arxiv{1001.2010}
